---
title: "Connectome Method"
author: "Eric Bridgeford"
date: "May 4, 2017"
output: html_document
---

Below, we first show an aggregation of the latest version of FNGS for our respective post-processing pipelines:

```{r}
  require(Discriminability)
  signal_overall <- c()
  ids_overall <- c()
  dataset_overall <- c()
  all_signals <- list()
```

# FNGS

## BNU1 EPI FNIRT

```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0530/BNU_1/epi_fnirt/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  all_signals[[1]] <- signal
  
  signal_overall <- c(signal)
  ids_overall <- c(rep('BNU1_epi_fnirt', length(signal)))
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```


## BNU1 EPI FLIRT

```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0530/BNU_1/epi_flirt/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  all_signals[[2]] <- signal
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, rep('BNU1_epi_flirt', length(signal)))
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```


## BNU1 FLIRT FNIRT

```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0530/BNU_1/flirt_fnirt/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  all_signals[[3]] <- signal
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, rep('BNU1_flirt_fnirt', length(signal)))
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```


## BNU1 FLIRT FLIRT

```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0530/BNU_1/flirt_flirt/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  all_signals[[4]] <- signal
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, rep('BNU1_flirt_flirt', length(signal)))
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```


## Overall CMP

```{r, fig.height=6, fig.width=12, message=FALSE}
tdr <- time_discr(signal_overall, ids_overall, rank=FALSE)
print(tdr$combinedplot)
```
