---
title: "Merging FNGS"
author: "Eric Bridgeford"
date: "March 13, 2017"
output: html_document
---

# BNU1

## Sanity Check

```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_merge/fngs_0410/ts_roi/desikan-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 3
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal)
  ids_overall <- c(ids)
```

### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
### Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cor(ts1), title=title, legend="corr"))
```

## Non Ranking

### Spectral Approach 

#### Raw Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  tr = 2.5
  lc = 0.01
  amp <- freq_discr(signal, ids, tr, lc, spec='amp', rank=FALSE)
  print(amp$combinedplot)
```

#### Raw Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  pow <- freq_discr(signal, ids, tr, lc, spec='pow', rank=FALSE)
  print(pow$combinedplot)
```

### Standard Discriminability Approach

#### Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

## Ranking

### Spectral Approach 

#### Ranked Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  ampr <- freq_discr(signal, ids, tr, lc, spec='amp', rank=TRUE)
  print(ampr$combinedplot)
```

#### Ranked Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  powr <- freq_discr(signal, ids, tr, lc, spec='pow', rank=TRUE)
  print(powr$combinedplot)
```

### Standard Discriminability Approach

#### Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

```{r }
  collection <- data.frame(dataset='BNU1', postprocessing=c('amp', 'power', 'corr', 'ramped', 'rpower', 'rcorr'),
                           discr=c(amp$d, pow$d, td$d, ampr$d, powr$d, tdr$d))
```

# DC1

## Non Ranking
```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_merge/DC1/roi_timeseries/desikan-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 3
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall)
```

## Sanity Check

### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
### Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cor(ts1), title=title, legend="corr"))
```

### Spectral Approach 

#### Raw Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  tr = 2.5
  lc = 0.01
  amp <- freq_discr(signal, ids, tr, lc, spec='amp', rank=FALSE)
  print(amp$combinedplot)
```

#### Raw Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  pow <- freq_discr(signal, ids, tr, lc, spec='pow', rank=FALSE)
  print(pow$combinedplot)
```

### Standard Discriminability Approach

#### Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

## Ranking

### Spectral Approach 

#### Ranked Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  ampr <- freq_discr(signal, ids, tr, lc, spec='amp', rank=TRUE)
  print(ampr$combinedplot)
```

#### Ranked Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  powr <- freq_discr(signal, ids, tr, lc, spec='pow', rank=TRUE)
  print(powr$combinedplot)
```

### Standard Discriminability Approach

#### Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

```{r }
  collection <- rbind(collection, data.frame(dataset='DC1', postprocessing=c('amp', 'power', 'corr', 'ramped', 'rpower', 'rcorr'),
                           discr=c(amp$d, pow$d, td$d, ampr$d, powr$d, tdr$d)))
```


# NKI1

## Non Ranking
```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_merge/NKI1/roi_timeseries/desikan-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 4
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall)
```

## Sanity Check

### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
### Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cor(ts1), title=title, legend="corr"))
```

### Spectral Approach 

#### Raw Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  tr = 1.4
  lc = 0.01
  amp <- freq_discr(signal, ids, tr, lc, spec='amp', rank=FALSE)
  print(amp$combinedplot)
```

#### Raw Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  pow <- freq_discr(signal, ids, tr, lc, spec='pow', rank=FALSE)
  print(pow$combinedplot)
```

### Standard Discriminability Approach

#### Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

## Ranking

### Spectral Approach 

#### Ranked Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  ampr <- freq_discr(signal, ids, tr, lc, spec='amp', rank=TRUE)
  print(ampr$combinedplot)
```

#### Ranked Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  powr <- freq_discr(signal, ids, tr, lc, spec='pow', rank=TRUE)
  print(powr$combinedplot)
```

### Standard Discriminability Approach

#### Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

```{r }
  collection <- rbind(collection, data.frame(dataset='NKI1', postprocessing=c('amp', 'power', 'corr', 'ramped', 'rpower', 'rcorr'),
                           discr=c(amp$d, pow$d, td$d, ampr$d, powr$d, tdr$d)))
```

# LMU1

## Non Ranking
```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_merge/LMU1/roi_timeseries/desikan-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 4
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall)
```

## Sanity Check

### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
### Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cor(ts1), title=title, legend="corr"))
```

### Spectral Approach 

#### Raw Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  tr = 2.5
  lc = 0.01
  amp <- freq_discr(signal, ids, tr, lc, spec='amp', rank=FALSE)
  print(amp$combinedplot)
```

#### Raw Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  pow <- freq_discr(signal, ids, tr, lc, spec='pow', rank=FALSE)
  print(pow$combinedplot)
```

### Standard Discriminability Approach

#### Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

## Ranking

### Spectral Approach 

#### Ranked Amplitude Spectrum

```{r, fig.height=6, fig.width=12, message=FALSE}
  ampr <- freq_discr(signal, ids, tr, lc, spec='amp', rank=TRUE)
  print(ampr$combinedplot)
```

#### Ranked Power Spectrum
```{r, fig.height=6, fig.width=12, message=FALSE}
  powr <- freq_discr(signal, ids, tr, lc, spec='pow', rank=TRUE)
  print(powr$combinedplot)
```

### Standard Discriminability Approach

#### Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

```{r }
  collection <- rbind(collection, data.frame(dataset='LMU1', postprocessing=c('amp', 'power', 'corr', 'ramped', 'rpower', 'rcorr'),
                           discr=c(amp$d, pow$d, td$d, ampr$d, powr$d, tdr$d)))
```

```{r, fig.height=6, fig.width=12, message=FALSE}
  collection$dataset <- factor(collection$dataset)
  collection$postprocessing <- factor(collection$postprocessing)
  summaryfig <- ggplot(collection, aes(x=postprocessing, y=discr, color=dataset)) +
    geom_point(size=4) +
    ggtitle('Comparing Discriminability over 4 reference datasets using different postprocessing techniques')
  print(summaryfig)
```

```{r, fig.height=6, fig.width=12, message=FALSE}
  summaryfig <- ggplot(collection, aes(x=postprocessing, y=discr, fill=postprocessing)) +
    geom_violin() +
    geom_boxplot(width=0.1) +
    ggtitle('Comparing Discriminability over 4 reference datasets using different postprocessing techniques')
  print(summaryfig)
```
