---
title: "Merging FNGS"
author: "Eric Bridgeford"
date: "May 4, 2017"
output: html_document
---

Below, we first show an aggregation of the latest version of FNGS for our respective post-processing pipelines:

```{r}
  require(Discriminability)
  signal_overall <- c()
  ids_overall <- c()
  cpac_graphs_overall <- c()
  cpac_ids_overall <- c()
  dataset_overall <- c()
```

# FNGS

## BNU1

```{r, fig.height=6, fig.width=12, message=FALSE}
  require(Discriminability)
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_merge/BNU1/roi_timeseries/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 3
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, tsobj$dataset)
  
  cpac_inpath <- 'C:/Users/ebrid/Documents/R/CPAC_results/BNU1/FSL_frf_nsc_ngs_des/'
  cpac_tsnames <- list.files(cpac_inpath, pattern="\\.graphml", full.names=TRUE)
  scan_pos = 2
  cpac_graobj <- open_graphs(cpac_tsnames, sub_pos=scan_pos)
  cpac_graphs <- cpac_graobj[[1]]
  cpac_ids <- cpac_graobj[[3]]
  
  cpac_graphs_overall <- c(cpac_graphs_overall, cpac_graphs)
  ids_overall <- c(ids_overall, cpac_graobj$dataset)
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### CPAC Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cpac_graphs[[1]], title=title, legend="corr"))
```



#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

#### CPAC Raw Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_td <- time_discr(cpac_graphs, cpac_ids, rank=FALSE, graphs = TRUE)
  print(cpac_td$combinedplot)
```

#### CPAC Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_tdr <- time_discr(cpac_graphs, cpac_ids, rank=TRUE, graphs = TRUE)
  print(cpac_tdr$combinedplot)
```

```{r }
  collection <- data.frame(dataset='BNU1',
                                             postprocessing=c('fngs_corr', 'fngs_rcorr',
                                                              'cpac_corr', 'cpac_rcorr'),
                           discr=c(td$d, tdr$d, cpac_td$d, cpac_tdr$d))
```

## DC1

```{r, fig.height=6, fig.width=12, message=FALSE}
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0503/DC1/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, tsobj$dataset)

  cpac_inpath <- 'C:/Users/ebrid/Documents/R/CPAC_results/DC1/FSL_frf_nsc_ngs_aal/'
  cpac_tsnames <- list.files(cpac_inpath, pattern="\\.graphml", full.names=TRUE)
  scan_pos = 2
  cpac_graobj <- open_graphs(cpac_tsnames, sub_pos=scan_pos)
  cpac_graphs <- cpac_graobj[[1]]
  cpac_ids <- cpac_graobj[[3]]
  
  cpac_graphs_overall <- c(cpac_graphs_overall, cpac_graphs)
  ids_overall <- c(ids_overall, cpac_graobj$dataset)
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### CPAC Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cpac_graphs[[1]], title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

#### CPAC Raw Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_td <- time_discr(cpac_graphs, cpac_ids, rank=FALSE, graphs = TRUE)
  print(cpac_td$combinedplot)
```

#### CPAC Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_tdr <- time_discr(cpac_graphs, cpac_ids, rank=TRUE, graphs = TRUE)
  print(cpac_tdr$combinedplot)
```

```{r }
  collection <- rbind(collection, data.frame(dataset='DC1',
                                             postprocessing=c('fngs_corr', 'fngs_rcorr',
                                                              'cpac_corr', 'cpac_rcorr'),
                           discr=c(td$d, tdr$d, cpac_td$d, cpac_tdr$d)))
```

## HNU1

```{r, fig.height=6, fig.width=12, message=FALSE}
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0503/HNU1/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, tsobj$dataset)

  cpac_inpath <- 'C:/Users/ebrid/Documents/R/CPAC_results/HNU1/FSL_frf_nsc_ngs_aal/'
  cpac_tsnames <- list.files(cpac_inpath, pattern="\\.graphml", full.names=TRUE)
  scan_pos = 2
  cpac_graobj <- open_graphs(cpac_tsnames, sub_pos=scan_pos)
  cpac_graphs <- cpac_graobj[[1]]
  cpac_ids <- cpac_graobj[[3]]
  
  cpac_graphs_overall <- c(cpac_graphs_overall, cpac_graphs)
  ids_overall <- c(ids_overall, cpac_graobj$dataset)
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### CPAC Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cpac_graphs[[1]], title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

#### CPAC Raw Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_td <- time_discr(cpac_graphs, cpac_ids, rank=FALSE, graphs = TRUE)
  print(cpac_td$combinedplot)
```

#### CPAC Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_tdr <- time_discr(cpac_graphs, cpac_ids, rank=TRUE, graphs = TRUE)
  print(cpac_tdr$combinedplot)
```

```{r}
  collection <- rbind(collection, data.frame(dataset='HNU1',
                                             postprocessing=c('fngs_corr', 'fngs_rcorr',
                                                              'cpac_corr', 'cpac_rcorr'),
                           discr=c(td$d, tdr$d, cpac_td$d, cpac_tdr$d)))
```

## NYU1

```{r, fig.height=6, fig.width=12, message=FALSE}
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0503/NYU1/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, tsobj$dataset)

  cpac_inpath <- 'C:/Users/ebrid/Documents/R/CPAC_results/NYU1/FSL_frf_nsc_ngs_aal/'
  cpac_tsnames <- list.files(cpac_inpath, pattern="\\.graphml", full.names=TRUE)
  scan_pos = 2
  cpac_graobj <- open_graphs(cpac_tsnames, sub_pos=scan_pos)
  cpac_graphs <- cpac_graobj[[1]]
  cpac_ids <- cpac_graobj[[3]]
  
  cpac_graphs_overall <- c(cpac_graphs_overall, cpac_graphs)
  ids_overall <- c(ids_overall, cpac_graobj$dataset)
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### CPAC Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cpac_graphs[[1]], title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

#### CPAC Raw Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_td <- time_discr(cpac_graphs, cpac_ids, rank=FALSE, graphs = TRUE)
  print(cpac_td$combinedplot)
```

#### CPAC Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_tdr <- time_discr(cpac_graphs, cpac_ids, rank=TRUE, graphs = TRUE)
  print(cpac_tdr$combinedplot)
```

```{r}
  collection <- rbind(collection, data.frame(dataset='NYU1',
                                             postprocessing=c('fngs_corr', 'fngs_rcorr',
                                                              'cpac_corr', 'cpac_rcorr'),
                           discr=c(td$d, tdr$d, cpac_td$d, cpac_tdr$d)))
```
## SWU4

```{r, fig.height=6, fig.width=12, message=FALSE}
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_2mm_0503/SWU4/aal-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 2
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, tsobj$dataset)

  cpac_inpath <- 'C:/Users/ebrid/Documents/R/CPAC_results/SWU4/FSL_frf_nsc_ngs_aal/'
  cpac_tsnames <- list.files(cpac_inpath, pattern="\\.graphml", full.names=TRUE)
  scan_pos = 2
  cpac_graobj <- open_graphs(cpac_tsnames, sub_pos=scan_pos)
  cpac_graphs <- cpac_graobj[[1]]
  cpac_ids <- cpac_graobj[[3]]
  
  cpac_graphs_overall <- c(cpac_graphs_overall, cpac_graphs)
  ids_overall <- c(ids_overall, cpac_graobj$dataset)
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### CPAC Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cpac_graphs[[1]], title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

#### CPAC Raw Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE}
  cpac_td <- time_discr(cpac_graphs, cpac_ids, rank=FALSE, graphs = TRUE)
  print(cpac_td$combinedplot)
```

#### CPAC Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  cpac_tdr <- time_discr(cpac_graphs, cpac_ids, rank=TRUE, graphs = TRUE)
  print(cpac_tdr$combinedplot)
```

## BNU2

```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  inpath <- 'C:/Users/ebrid/Documents/R/fngs_merge/BNU2/roi_timeseries/desikan-2mm/'
  tsnames <- list.files(inpath, pattern="\\.rds", full.names=TRUE)
  scan_pos = 3
  tsobj <- open_timeseries(tsnames, sub_pos=scan_pos, exclude = TRUE)
  signal <- tsobj[[1]]
  ids <- tsobj[[3]]
  
  signal_overall <- c(signal_overall, signal)
  ids_overall <- c(ids_overall, tsobj$dataset)

  cpac_inpath <- 'C:/Users/ebrid/Documents/R/CPAC_results/BNU2/FSL_frf_nsc_ngs_des/'
  cpac_tsnames <- list.files(cpac_inpath, pattern="\\.graphml", full.names=TRUE)
  scan_pos = 2
  cpac_graobj <- open_graphs(cpac_tsnames, sub_pos=scan_pos)
  cpac_graphs <- cpac_graobj[[1]]
  cpac_ids <- cpac_graobj[[3]]
  
  cpac_graphs_overall <- c(cpac_graphs_overall, cpac_graphs)
  ids_overall <- c(ids_overall, cpac_graobj$dataset)
```

### Sanity Check

#### Timeseries

```{r fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  ts1 = signal[[1]]
  title = paste('Timeseries plot for subject', ids[1])
  print(plot_timeseries(ts1, title=title))

```
#### FNGS Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(abs(cor(ts1)), title=title, legend="corr"))
```

#### CPAC Correlation Matrix

```{r  fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  title = paste('Correlation plot for subject', ids[1])
  print(plot_square(cpac_graphs[[1]], title=title, legend="corr"))
```

#### FNGS Raw Correaltion Graphs
```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  td <- time_discr(signal, ids, rank=FALSE)
  print(td$combinedplot)
```

#### FNGS Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  tdr <- time_discr(signal, ids, rank=TRUE)
  print(tdr$combinedplot)
```

#### CPAC Raw Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  cpac_td <- time_discr(cpac_graphs, cpac_ids, rank=FALSE, graphs = TRUE)
  print(cpac_td$combinedplot)
```

#### CPAC Ranked Correlation Graphs
```{r, fig.height=6, fig.width=12, message=FALSE, eval=FALSE}
  cpac_tdr <- time_discr(cpac_graphs, cpac_ids, rank=TRUE, graphs = TRUE)
  print(cpac_tdr$combinedplot)
```

```{r, eval=FALSE}
  collection <- rbind(collection, data.frame(dataset='HNU1',
                                             postprocessing=c('fngs_corr', 'fngs_rcorr',
                                                              'cpac_corr', 'cpac_rcorr'),
                           discr=c(td$d, tdr$d, cpac_td$d, cpac_tdr$d)))
```

```{r, fig.height=6, fig.width=12, message=FALSE}
  collection$dataset <- factor(collection$dataset)
  collection$postprocessing <- factor(collection$postprocessing)
  summaryfig_fng <- ggplot(collection, aes(x=postprocessing, y=discr, color=dataset)) +
    geom_point(size=4) +
    ggtitle('Comparing Discriminability over 4 reference datasets using different postprocessing techniques')
  print(summaryfig_fng)
```

```{r, fig.height=6, fig.width=12, message=FALSE}
  summaryfig_fng <- ggplot(collection, aes(x=postprocessing, y=discr, fill=postprocessing)) +
    geom_violin() +
    geom_boxplot(width=0.1) +
    ggtitle('Comparing Discriminability over 4 reference datasets using different postprocessing techniques')
  print(summaryfig_fng)
```
